Thermodynamic fragments in magic state theories

### 2020-11-03 magic_paper.tex
minor changes

The final state Lorenz curve consists of $9^k (< 9^n)$ points, however, since we work in the unital fragment, the maximally mixed state $\frac{1}{d}\id$ is free, so can add in arbitrary many copies to the final state. 
This addition does not change the total Lorenz curve of the state, but merely increases the resolution on the $x$-axis. 
We thus want to compute the Lorenz curve of the state
\begin{equation}
\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k} \otimes \left( \frac{1}{d}\id\right)^{\otimes(n-k)},
\end{equation}
with transformed Wigner components 
\begin{equation}
w_j^\prime = \frac{1}{d^{2(n-k)}}w_j,
\end{equation}
and multiplicities $c_j^\prime = d^{2(n-k)}c_j$, where $w_j, c_j$ are given in~\cref{tab:lcsu_w} for $j=0,\dots,k$. \ddd{[DJ: You've been too sloppy and rushed here. Give the explicit definition of $w'_j$. You've hit a problem almost certainly because you are not handling this technical bit carefully and explicitly - it is crucial, so really unpack it slowly!]}

Let's look at an example in~\cref{fig:lc_compare}.
The Lorenz curve of the final state $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2}$ remains the same when we rewrite the state as $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2} \otimes (\tfrac{1}{3} \id)^{\otimes 2}$, but now it consists of $9^4$ points with the same $x$-coordinates as the initial state. \ddd{[DJ: I don't think this is true. You should step through the computation of the Lorenz curve more carefully and see why]}.
The line segment between elbows $x_0 = 0$ and $x_1 = 1/9^2$ consists only of its endpoints for state $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2}$.
However, for state $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2} \otimes \left( \tfrac{1}{3} \id\right)^{\otimes 2}$ it consists of $82$ points with coordinates $(k/9^4, kw_0)$ for $k=0,\dots,9^2$.
The same reasoning applies on all three line segments comprising the Lorenz curve.
\begin{figure}[t]
    \centering
    \includegraphics[scale=0.6]{figs/lc_compare.pdf}
    \caption{\textbf{Example of Lorenz curve comparison.} 
    The upper Lorenz curve (blue -- $n=4$ and $\epsilon = 0.20$) is always higher than the lower Lorenz curve (red -- $k=2$ and $\epsilon_\tau = 0.05$).
    }
    \label{fig:lc_compare}
\end{figure}
Therefore, we can compare the curves pointwise with $9^n + 1$ inequalities of the form
\begin{equation}\label{eq:lc_pointwise}
\lc{\noisysn}{\frac{1}{d}\id}(x) \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x)
\end{equation}
for all $x \in X$.

@@

The RHSs can be calculated directly by~\cref{lc_coord_elb}, but the LHSs do not correspond to elbows.
To calculate $\lc{\noisysn}{\frac{1}{d}\id}(x_j)$ for $j=1,\dots,k$, we first need to identify the elbow of the curve just before $x_j$.
Let $R \coloneqq \{x^{(\rho)}_0, x^{(\rho)}_1, \dots, x^{(\rho)}_n, x^{(\rho)}_{n+1}\} \subset X$ be the elbows of $\lc{\noisysn}{\frac{1}{d}\id}(x)$.
Then, the elbow index just before $x_j$ is
\begin{equation}
	J = \max{\{i: x^{(\rho)}_i \leq x_j \}}.
\end{equation}
The slope from the $J$-th elbow to point $(x_j, \lc{\noisysn}{\frac{1}{d}\id}(x_j)$ is given by the $(J+1)$-th Wigner component, so that the LHS can be calculated as 
\begin{equation}\label{calc_lhs}
	L_J + d^{2n}(x_j - x_J)w_{J+1}.
\end{equation}
This is illustrated in~\cref{fig:lc_compare}, where we check the constarint at $x_2 = 0.8025$.
Using~\cref{lc_coord_elb}, we find that $\lc{\rho_{\rm{S}}(\epsilon_\tau)^{\otimes 2}}{\frac{1}{d}\id}(x_2) = 1.8158$, while expression~\cref{calc_lhs} gives $\lc{\rho_{\rm{S}}(\epsilon)^{\otimes 4}}{\frac{1}{d}\id}(x_2) = 2.235$.

>>>>

The final state Lorenz curve consists of $9^k (< 9^n)$ points, however, since we work in the unital fragment, the maximally mixed state $\frac{1}{d}\id$ is free, so can add in arbitrary many copies to the final state. 
This addition does not change the total Lorenz curve of the state, but merely increases the resolution on the $x$-axis. 
We thus want to compute the Lorenz curve of the state
\begin{equation}
\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k} \otimes \left( \frac{1}{d}\id\right)^{\otimes(n-k)},
\end{equation}
with transformed Wigner components 
\begin{equation}
w_j^\prime = \frac{1}{d^{2(n-k)}}w_j,
\end{equation}
and multiplicities $c_j^\prime = d^{2(n-k)}c_j$, where $w_j, c_j$ are given in~\cref{tab:lcsu_w} for $j=0,\dots,k$. 
\ddd{[DJ: You've been too sloppy and rushed here. Give the explicit definition of $w'_j$. You've hit a problem almost certainly because you are not handling this technical bit carefully and explicitly - it is crucial, so really unpack it slowly!]} \nick{I don't think it gets more explicit, you just split the line segments uniformly into $d^{2(n-k)}$ segments of length equal to $1/d^{2(n-k)}$ of the total length.}

Let's look at an example in~\cref{fig:lc_compare}.
The Lorenz curve of the final state $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2}$ remains the same when we rewrite the state as $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2} \otimes (\tfrac{1}{3} \id)^{\otimes 2}$, but now it consists of $9^4$ points with the same $x$-coordinates as the initial state.
The line segment between elbows $x_0 = 0$ and $x_1 = 1/9^2$ consists only of its endpoints for state $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2}$.
However, for state $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2} \otimes \left( \tfrac{1}{3} \id\right)^{\otimes 2}$ it consists of $82$ points with coordinates $(k/9^4, kw_0)$ for $k=0,\dots,9^2$.
The same reasoning applies on all three line segments comprising the Lorenz curve.
\begin{figure}[t]
    \centering
    \includegraphics[scale=0.6]{figs/lc_compare.pdf}
    \caption{\textbf{Example of Lorenz curve comparison.} 
    The upper Lorenz curve (blue -- $n=4$ and $\epsilon = 0.20$) is always higher than the lower Lorenz curve (red -- $k=2$ and $\epsilon_\tau = 0.05$).
    }
    \label{fig:lc_compare}
\end{figure}
Therefore, we can compare the curves pointwise with $9^n + 1$ inequalities of the form
\begin{equation}\label{eq:lc_pointwise}
\lc{\noisysn}{\frac{1}{d}\id}(x) \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x)
\end{equation}
for all $x \in X$.

@@

The RHSs can be calculated directly by~\cref{lc_coord_elb}, but the LHSs do not correspond to elbows.
To calculate $\lc{\noisysn}{\frac{1}{d}\id}(x_j)$ for $j=1,\dots,k$, we first need to identify the elbow of the curve just before $x_j$.
Let $R \coloneqq \{y_0, y_1, \dots, y_n, y_{n+1}\} \subset X$ be the elbows of $\lc{\noisysn}{\frac{1}{d}\id}(x)$.
Then, the elbow index just before $x_j$ is
\begin{equation}
	J = \max{\{i: y_i \leq x_j \}}.
\end{equation}
The slope from the $J$-th elbow to point $(x_j, \lc{\noisysn}{\frac{1}{d}\id}(x_j)$ is given by the $(J+1)$-th Wigner component, so that the LHS can be calculated as 
\begin{equation}\label{calc_lhs}
	L_J + d^{2n}(x_j - x_J)w_{J+1}.
\end{equation}
This is illustrated in~\cref{fig:lc_compare}, where we check the constarint at $x_2 = 0.8025$.
Using~\cref{lc_coord_elb}, we find that $\lc{\rho_{\rm{S}}(\epsilon_\tau)^{\otimes 2}}{\frac{1}{d}\id}(x_2) = 1.8158$, while expression~\cref{calc_lhs} gives $\lc{\rho_{\rm{S}}(\epsilon)^{\otimes 4}}{\frac{1}{d}\id}(x_2) = 2.235$.
